---
title: "Beijing PM2.5 Analysis"
output: 
    html_document:
        toc: FALSE
---

```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)
library(lubridate)

# INITALIZE CODE CHUNK OPTIONS
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = FALSE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```


```{css, echo = FALSE}
.code-r { /* Code block */
  font-size: 15px;
}

.code-r-small { /* Code block */
  font-size: 10px;
}
```

```{r load-data}
source("process_pm25_data.R")
```


<br>

## Association between PM2.5 concentration and temperature

Now we will look examine the relationship between PM2.5 concentration and temperature. By previous studies done by myself (Hua, 2022), time of the day can significantly influence Pm2.5. Therefore, we will draw three trend lines (PM2.5 concentration vs. temperature) grouped by time of the day.

```{r plot2, class.source="code-r-small"}
data %>%
  plot_ly(x = ~temp, y = ~pm25, color = ~day_part, type = "scatter")
```

The plot above shows a trend that suggests the PM2.5 concentration decreases as temperature increases. 

<br>

## Association between PM2.5 distribution and time of the day

Here we will look at the distributions of PM2.5 concentration with histograms. Further, we will group the data by time of the day (morning, afternoon, and evening) and put the histograms side by side to see the difference. 

```{r plot3, class.source="code-r-small"}
data %>%
  group_by(day_part) %>%
  do(p = plot_ly(., x = ~pm25, name = ~day_part, type = "histogram")) %>%
  subplot(nrows = 1, shareX = TRUE, shareY = TRUE)
```

From the figure above, we can see that while all PM2.5 concentration distributions are right skewed with a mode close to 0, the afternoon distribution is more skewed with and has fewer high-PM2.5 entries. 

<br>

## References

Hua, Qiwen. (2022). *Association between PM2.5 concentration and other meteorological factors* [Unpublished assignment submitted for JSC370]. University of Toronto.

<br>
<br>










