---
title: "Beijing PM2.5 Analysis"
author: "Qiwen Hua"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

<br>

This is my JSC370 Homework 5 website. I will showcase a few interactive visuals on the Beijing PM2.5 data here.

<br>

```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)
library(lubridate)

# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = FALSE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```

```{css, echo = FALSE}
.code-r { /* Code block */
  font-size: 15px;
}

.code-r-small { /* Code block */
  font-size: 10px;
}
```

<br>

## Overview

The dataset that we will use throughout this analysis comes from the [UCI Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/Beijing+PM2.5+Data) gathered by Liang, X. et al (2015). The dataset contains hourly meteorological data from 2010 Jan 1st to 2014 Dec 31st of US Embassy in Beijing, which includes information such as the PM2.5 concentration, dew point, temperature, wind speed, etc. Among those features, listed below are our interested variables and their corresponding units: 

  1. PM2.5 concentration (μg/m³);
  2. Hour of the day;
  3. Dew point (°C);
  4. Temperature (°C);
  5. Wind speed (m/s).
  
Building from the raw data, I also created some categorical variables for later uses including "low", "normal", "high" categories for meteorological metrics, time of the day, and air quality. 
  
Note that the above information is gather by myself in *Association between PM2.5 concentration and other meteorological factors* submitted for JSC370 midterm project. 

```{r load-data}
source("process_pm25_data.R")
```

<br>

## PM2.5 Trend

The figure below shows the trend of PM2.5 concentration in Beijing, China along with a smoothened trend line for built with GAM. 

I created the figure below by directly converting my previous ggplot figure to a plotly interactive figure. This method is chosen here to preserve the smoothened curve constructed by ggplot. For more native plotly figures that demonstrate the association between PM2.5 concentration and meteorological data, please visit the other page using the nav bar. 

```{r plot1, class.source="code-r-small"}
# Timeseries plot
p1_timeseries_gg <- data %>%
  ggplot(aes(datetime, pm25)) +
  ggtitle("Time series of PM2.5 concentration in Beijing, China") +
  geom_line() +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs", k = 40))

ggplotly(p1_timeseries_gg)
```

<br>

## References

Liang, X., Zou, T., Guo, B., Li, S., Zhang, H., Zhang, S., Huang, H. and Chen, S. X. (2015). *Assessing Beijing's PM2.5 pollution: severity, weather impact, APEC and winter heating*. Proceedings of the Royal Society A, 471, 20150257.

Hua, Qiwen. (2022). *Association between PM2.5 concentration and other meteorological factors* [Unpublished assignment submitted for JSC370]. University of Toronto.

<br>
<br>